
---
output:
  html_document:
    df_print: paged
  pdf_document: default
header-includes: \usepackage{color}
---
----
OKC Thunder Data Science & Solutions Technical Assessment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = F, results = 'hide', message=F, warning = F}
library(foreign)      #Default package for almost all code, lets your read files into R
library(ggplot2)      #plotting package
library(colorspace)   #better colors for ggplot
library(broom)        #a widely used, but relatively new, package for producing tidier data and tidier output; part of tidyverse
library(tidyverse)    #a widely used, but relatively new, package for producing tidier data and tidier output
library(knitr)        #helps the knitting process. In particular, it lets the include_graphics command run
library(scales)
library(knitr)
library(modelr)
```

# Data Science & Solutions Technical Assessment

### Author:
Eric Wnorowski

## Deliverables
Determine the shot zones (2PT, NC3 or C3) and calculate for each team the:
  1) Shot Distribution: the percentage of team shots attempted within a zone
  2) eFG%: the effective field goal percentage of team shots within a zone
  
### Import Data
```{r, echo = T, results = 'hide', message=F, warning = F}
shots <- read.csv("Datasets/shots_data.csv")
```

### Filter Data
```{r}
shotsA <- shots %>%
  filter(team == "Team A")
shotsB <- shots %>%
  filter(team == "Team B")
```

## Finding Shot Distribution
For all “Non Corner” 3’s (where Y > 7.8), the 3PT line is 23.75 ft from the center of the hoop
For all “Corner” 3’s (where Y <= 7.8), the 3PT line is 22 feet from the court’s Y-axis at all
points (note the definition of “Corner” 3 is not determined by the “break” in the arc)

### Filter Data
```{r}
shotsAC3 <- shotsA %>%
  filter((x > 22 & y < 7.8) | (x < -22 & y < 7.8))

summary(shotsAC3)

shotsANC3 <- shotsA %>%
  filter((x > 23.75 & y > 7.7)  | (x < -23.75 & y > 7.7))

summary(shotsANC3)

shotsA2PT <- shotsA %>%
  filter(y > 7.8 | (y < 7.8 & (x < 22 & x > -22)))

summary(shotsA2PT)
```

```{r}
shotsBC3 <- shotsB %>%
  filter((x > 22 & y < 7.8) | (x < -22 & y < 7.8))

summary(shotsBC3)

shotsBNC3 <- shotsB %>%
  filter((x > 23.75 & y > 7.7)  | (x < -23.75 & y > 7.7))

summary(shotsBNC3)

shotsB2PT <- shotsB %>%
  filter(y > 7.7 | (y < 7.8 & (x < 22 & x > -22)))

summary(shotsB2PT)
```

### Distribution

It appears that neither team attempted a Non-Corner 3. No shot in the entire dataset has x > 23.75 which is the minimum needed for it to be considered a Non-Corner 3. Meaning each team only took a Corner Three or a 2 pointer.

Summary Statistics show that there are 280 shots for Team A and 280 for Team B. 

For Team A summary shows 20 Corner 3 shots: 20/280 = .07142857 or 7.142857% of their shots are Corner Threes, meaning that: 260/280 = .92857143 or 92.857143% of there shots are two pointers.

For Team B summary shows 21 Corner 3 shots: 21/280 = .075 or 7.5% of their shots are Corner Threes, meaning that: 259/280 = .925 or 92.5% of their shots were two pointers.

## Finding eFG%

eFG% = (FGM + (0.5 x 3PM)) / FGA

### Team A

Corner 3
```{r}
sum(with(shotsAC3,fgmade == "1"))
```
eFG% = (8 + (0.5 x 8)) / 20 = 0.6 or 60%

2 Point
```{r}
sum(with(shotsA2PT,fgmade == "1"))
```
eFG% = (97 + (0.5 x 0)) / 260 = 0.3731 or 37.31%

Non-Corner 3
eFG% = (0 + (0.5 x 0)) / 0 = 0%


### Team B

Corner 3
```{r}
sum(with(shotsBC3,fgmade == "1"))
```
eFG% = (5 + (0.5 x 5)) / 21 = 0.3571 or 35.71%

2 Point
```{r}
sum(with(shotsB2PT,fgmade == "1"))
```
eFG% = (110 + (0.5 x 0)) / 259 = 0.4247 or 42.47%

Non-Corner 3
eFG% = (0 + (0.5 x 0)) / 0 = 0%

